Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-15 paper/manuscript.Rmd
Q5 and Morris citation

The trade-off associated with swimming between islands can be understood as
density-dependent habitat selection governed by the Ideal Free Distribution
[@Morris1987; @Bradbury2015]. Ideal Free Distribution theory predicts a fitness
equilibrium: when the density in a given habitat patch has exceeded the optimum
for fitness within that patch, animals should relocate and settle new habitat
patches, so that fitness is equal across all patches [@Bradbury2015]. Islands
act as discrete habitat patches in this case, but the costs associated with
swimming create a trade-off when moving between patches. For caribou in the Fogo
Island archipelago, the role of forage limitation in habitat selection patterns
remains unknown, but swimming between islands may be at least partially governed
by density-dependent habitat selection.

@@

5) In relation to all the previous questions: how do individuals vary in their
assessment of the costs and benefits of swimming between islands? Why did some
caribou regularly engage in swimming events, while more than half of our marked
population were never observed swimming in the ocean? The forage limitation
hypothesis is thought to apply uniformly across populations, but individual
caribou could evaluate the costs and benefits of swimming differently. It is
possible that some individuals, in our case ~10%, considered swimming to be less
costly or perceived competition or predation more acutely than their
conspecifics.

>>>>

The trade-off associated with swimming between islands can be understood as
density-dependent habitat selection governed by the Ideal Free Distribution
[@Morris1987]. Ideal Free Distribution theory predicts a fitness
equilibrium: when the density in a given habitat patch has exceeded the optimum
for fitness within that patch, animals should relocate and settle new habitat
patches, so that fitness is equal across all patches [@Morris1987]. Islands
act as discrete habitat patches in this case, but the costs associated with
swimming create a trade-off when moving between patches. For caribou in the Fogo
Island archipelago, the role of forage limitation in habitat selection patterns
remains unknown, but swimming between islands may be at least partially governed
by density-dependent habitat selection.

@@

5) In relation to all the previous questions: how do individuals vary in their
propensity to swim and their assessment of the costs and benefits of swimming
between islands? We observed some individuals that regularly engaged in swimming
events, while others were never observed swimming in the ocean? Our existing research on individual behavioural variation in caribou movement ecology The forage
limitation hypothesis is thought to apply uniformly across populations, but
individual caribou could evaluate the costs and benefits of swimming
differently. It is possible that some individuals, in our case ~10%, considered
swimming to be less costly or perceived competition or predation more acutely
than their conspecifics.
